The NIME of the Title Is Hello

### 2025-01-15 src/article.tex
add ethical standards template

@@

\section{Reference}\label{reference}

>>>>

\section{Ethical Standards}\label{ethical-standards}

To ensure objectivity and transparency in research and to ensure that
accepted principles of ethical and professional conduct have been
followed, authors must include a section ``Ethical Standards'' before
the References. This section should include (if relevant): information
regarding sources of funding, potential conflicts of interest (financial
or non-financial), informed consent if the research involved human
participants, statement on welfare of animals if the research involved
animals or any other information or context that helps ethically situate
your research. For help with the ethics section, feel free to ask on the
NIME forum: \url{https://forum.nime.org}.

@@
